TITLE

### 2021-02-18 outputs/paper/paper.Rmd

@@

* Demographic information
- Disability status
- Indigenous status
- Visible minority (non-Indigenous) status
* Type of service provided (dine-in, take-out, or both)
* Revenue in May 2021
* Employees
- Number of full-time employees (30 hours/week or more)
- Number of part-time employees (less than 30 hours/week)
* Applications for government assistance
- Which funds were applied for
- Estimated money received

@@

* Demographic information
- Disability status
- Indigenous status
- Visible minority (non-Indigenous) status
* Type of service provided (dine-in, take-out, or both)
* Closures (none, temporary, or permanent)
* Revenue in May 2021
* Employees
- Number of full-time employees (30 hours/week or more)
- Number of part-time employees (less than 30 hours/week)
* Applications for government assistance
- Which funds were applied for
- Estimated money received

@@

### FINDING ONE
 Closures had a negative impact

@@

### FINDING THREE
CLosures had a stronger negative impact on POC-owned

@@

@@

>>>>

This survey cost <<<<<<<<LORENA>>>>>>>>>>>>>.

@@

* Demographic information
- Disability status
- Indigenous status
- Visible minority (non-Indigenous) status
- Gender identity
* Type of service provided (dine-in, take-out, or both)
* Revenue in May 2021
* Employees
- Number of full-time employees (30 hours/week or more)
- Number of part-time employees (less than 30 hours/week)

@@

* Demographic information
- Disability status
- Indigenous status
- Visible minority (non-Indigenous) status
- Gender identity
* Type of service provided (dine-in, take-out, or both)
* Closures (none, temporary, or permanent)
* Revenue in May 2021
* Employees
- Number of full-time employees (30 hours/week or more)
- Number of part-time employees (less than 30 hours/week)

Survey 1 data as baseline

Counterfactuals

Survey 2 data to contrast treatment and control.

@@

### FINDING ONE
Closures had a negative impact on revenues and employment counts

Suggestion: funding for businesses and temporary unemployment

@@

Suggestions: technical support for restaurants to increase takeout business

### FINDING THREE
Closures had a stronger negative impact on indigenous or visible minority-owned businesses.

Suggestions: grants for minority business owners

@@

External validity, internal validity, cluster sampling. Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them.

Legally registered businesses only.

Survey non-response.

Self-reported information.

@@

For statistical analysis, this would require propensity score weighting.

# Appendix {-}
